Stage-Splitting a Modal Language

### 2014-10-11 paper/relatedwork.tex
added a quick preamble to the related work

\section{Related Work}

Partial evaluation is a well-studied technique for specializing programs to some of their input.  
The usual phrasing of the partial evaluation problem implicitly includes binding time analysis,
but many presentations start with a stage-annotated representation, as we have done.
We've shown that our dynamic semantics can be used to perform partial evaluation 
[need to do more reading to know exactly how it compares].

>>>>

\section{Related Work}
There are several distinctive aspect of our work which we wish to compare and contrast.
Firstly, \lang\ is a simply typed lambda calculus 
with explicit stage annotations and a non-duplicating semantics.
Its statics and dynamics enforce no backward information flow,
which a is necessary property to define a splitting transformation
that is equivalent to the dynamics.
Finally, the splitting transformation itself operates on any well-typed open term in \lang.

Partial evaluation is a well-studied technique for specializing programs to some of their input.  
Often, the goal of partial evaluation systems is to go all the way from unstaged code to a specialized version.
Although this problem definition implicitly includes binding time analysis,
many presentations factor out that step and start with a stage-annotated representation, as we have done.
We've shown that our dynamic semantics can be used to perform partial evaluation 
[need to do more reading to know exactly how it compares].
